Domain-agnostic Outlier Ranking Algorithms (DORA)---A Configurable Pipeline for Facilitating Outlier Detection in Scientific Datasets

### 2021-09-19 publications/iaai21/dora_outlier_detection_iaai.tex
Comment out acknowledgements due to page limits, will add to camera ready later. #42

%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\title{Domain-agnostic Outlier Ranking Algorithms (DORA)---A Configurable Pipeline for Facilitating Outlier Detection in Scientific Datasets}
\author {
    % Authors
    Hannah Kerner,\textsuperscript{\rm 1}
    Umaa Rebbapragada, \textsuperscript{\rm 2}
    Kiri Wagstaff, \textsuperscript{\rm 2} 
    Steven Lu, \textsuperscript{\rm 2} 
    Bryce Dubayah, \textsuperscript{\rm 1} \\
    Eric Huff, \textsuperscript{\rm 2} 
    Jake Lee, \textsuperscript{\rm 2} 
    Vinay Raman, \textsuperscript{\rm 3}
    Sakshum Kulshrestha \textsuperscript{\rm 1}  \\
}
\affiliations {
    % Affiliations
    \textsuperscript{\rm 1} University of Maryland, College Park \\
    \textsuperscript{\rm 2} Jet Propulsion Laboratory, 
    									   California Institute of Technology \\
    \textsuperscript{\rm 3} Montgomery Blair High School \\
    \{hkerner\}@umd.edu, \{umaa.d.rebbapragada,
    										kiri.l.wagstaff,
    										you.lu,
    										eric.m.huff\}@jpl.nasa.gov
}

@@

@@

\section{Acknowledgments}
We thank the NASA Center Innovation Fund and the NASA Science Mission 
Directorate (under the NASA Cross-Divisional AI Use Case Demonstration grants)
 for supporting this work.

\todo{Acknowledge DES?}
We thank the UN Food and Agriculture Organization (FAO) and Dr. Ritvik Sahajpal
(University of Maryland/NASA Harvest) for providing the maize ground
 observation dataset.

We thank Raymond Francis for analyzing the Navcam rover images to
identify targets considered to be ``novel'' for evaluating outlier
detection in the planetary rover scenario.

Part of this research was carried out at the Jet Propulsion
Laboratory, California Institute of Technology, under a contract with
the National Aeronautics and Space Administration.

>>>>

%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\title{Domain-agnostic Outlier Ranking Algorithms (DORA)---A Configurable Pipeline for Facilitating Outlier Detection in Scientific Datasets}
\author {
    % Authors
    Hannah Kerner,\textsuperscript{\rm 1}
    Umaa Rebbapragada, \textsuperscript{\rm 2}
    Kiri Wagstaff, \textsuperscript{\rm 2} 
    Steven Lu, \textsuperscript{\rm 2} 
    Bryce Dubayah, \textsuperscript{\rm 1} \\
    Eric Huff, \textsuperscript{\rm 2} 
    Jake Lee, \textsuperscript{\rm 2} 
    Vinay Raman, \textsuperscript{\rm 3}
    Sakshum Kulshrestha \textsuperscript{\rm 1}  \\
}
\affiliations {
    % Affiliations
    \textsuperscript{\rm 1} University of Maryland, College Park \\
    \textsuperscript{\rm 2} Jet Propulsion Laboratory, 
    									   California Institute of Technology \\
    \textsuperscript{\rm 3} Montgomery Blair High School \\
    hkerner@umd.edu, \{umaa.d.rebbapragada,
    										kiri.l.wagstaff,
    										you.lu,
    										eric.m.huff,
    										jake.h.lee\}@jpl.nasa.gov
}

@@

%\section{Acknowledgments}
%We thank the NASA Center Innovation Fund and the NASA Science Mission 
%Directorate (under the NASA Cross-Divisional AI Use Case Demonstration grants)
% for supporting this work.
%
%We thank the UN Food and Agriculture Organization (FAO) and Dr. Ritvik Sahajpal
%(University of Maryland/NASA Harvest) for providing the maize ground
% observation dataset.
% 
% We thank Raymond Francis for analyzing the Navcam rover images to
%identify targets considered to be ``novel'' for evaluating outlier
%detection in the planetary rover scenario.
%
%Part of this research was carried out at the Jet Propulsion
%Laboratory, California Institute of Technology, under a contract with
%the National Aeronautics and Space Administration.

@@
